 Sin and The City: Investigating the Number and Sex of Victims of Crimes Against the Person in Toronto Across 2014-2021.

### 2023-02-03 outputs/paper/Paper 1.qmd
Toronto Victimization: Fifth commit, includes all updated sub-folders and final deliverable

^[Code and data supporting this analysis is available at: LINK]

@@

knitr::kable(mean_data,
             "simple", 
             caption = "Average number of victims of crimes in Toronto across 2014                         -2021, grouped by category of crime", 
             col.names=c("Category of Crime", "Average Number of Victims"), 
             align=c('l', 'c'))

@@

knitr::kable(head(sex_data), 
             "simple", 
             caption = "The first 6 rows of the data frame used to represent the                           sex of the number of victims according to category of crime in Toronto Across 2014 - 2021", col.names=c("Sub-Category of Crime", "Sex", "Year", "Number of Victims"), 
             align=c('l', 'c', 'c'))

>>>>

^[Code and data supporting this analysis is available at: https://github.com/SofiaSellitto/Toronto-Victimization-Rates]

@@

knitr::kable(mean_data,
             "simple", 
             caption = "Average number of victims of crimes in Toronto across 2014-2021, grouped by category of crime", 
             col.names=c("Category of Crime", "Average Number of Victims"), 
             align=c('l', 'c'))

@@

knitr::kable(head(sex_data), 
             "simple", 
             caption = "The first 6 rows of the data frame used to represent thesex of the number of victims according to category of crime in Toronto Across 2014 - 2021", col.names=c("Sub-Category of Crime", "Sex", "Year", "Number of Victims"), 
             align=c('l', 'c', 'c', 'c'))
